A perfect storm and the natural endowments of trade-enabling infrastructure

### 2023-06-07 Slides/20min/20min.Rmd
Update slides

---
name: matching_coins
#### Coin findings (matched sample)

![Arch coins matched](Figures/arch_dummy_coins_matched.png)
[Back](#arch1)
---
name: matching_buildings
#### Building findings (matched sample)
![Arch buildings matched](Figures/arch_dummy_buildings.png)
[Back](#arch1)
---
### Safer, more convenient harbours
![Skudehandel](Figures/Wikimedia_skudehandel.jpg)
*Dangerous loading on the west coast*

>>>>

---
name: matching_coins
#### Coin findings (matched sample)
```{r echo=FALSE, out.width="80%", fig.align='center'}
knitr::include_graphics("Figures/arch_dummy_coins_matched.png")
```
[Back](#arch1)
---
name: matching_buildings
#### Building findings (matched sample)
```{r echo=FALSE, out.width="80%", fig.align='center'}
knitr::include_graphics("Figures/arch_dummy_buildings.png")
```
[Back](#arch2)
---
### Safer, more convenient harbours
![Skudehandel](Figures/Wikimedia_skudehandel.jpg)
*Dangerous loading on the west coast*
